---
title: "MuSiC Subclass Estimates - 20210208"
output: html_notebook
---

```{r warning=FALSE}
library(MuSiC)
library(dplyr)
library(vroom)
library(stringr)
library(janitor)
library(xbioc)

inputs <- paste0(getwd(), "/inputs/")
outputs <- paste0(getwd(), "/outputs/")
options(digits=3, scipen = 999)
```

# Functions
These will need to be modified from the methods functions because I'm no longer attempting to look at inter-seed variability. 

#### Extract Subsample IDs
```{r}
get_subsample <- function(id, sex, num, seed){
  for(s in sex){
    print(paste("Running the script on", s, "mice."))
  for(i in seed){
    print(paste("Sampling seed id:", i))
    set.seed(i)
  for(x in num){
    print(paste("Sampling a maximum of", x, "cells per cell type"))
    results_list <- list()
    z <- 1
    for(c in id){
      num_ids <- length(id)
      print(paste("Extracting ids for", c, "cells"))
      
      out <- as_tibble(filter(allen_metadata_2, sub_id == c & donor_sex_label == s))
      n_out <- length(which(out$sub_id == c))
      print(paste("There are", n_out, c, "cells total."))
        
      if(n_out >= x){
        out <- sample_n(out, x)
      }
        
      if(n_out < x){
          out <- sample_n(out, n_out)
      }
      results_list[[z]] <- out
      z <- z + 1
      }
    results <- bind_rows(results_list)
    results <- results %>%
      dplyr::select(sample_name)
    filename <- paste0(i, "-", x, "-", s, ".txt")
    print(paste("Writing results:", filename))
      
    write.table(results$sample_name, file = paste0(outputs, filename),
                  quote = FALSE, row.names = FALSE, col.names = FALSE,
                  sep = "\t")
      }
    }
  }
}

# Use this version to get ALL subclasses 
get_subsample_subclass <- function(id, num, seed){
  for(s in sex){
    print(paste("Running the script on", s, "mice."))
  for(i in seed){
    print(paste("Sampling seed id:", i))
    set.seed(i)
  for(x in num){
    print(paste("Sampling a maximum of", x, "cells per cell type"))
    results_list <- list()
    z <- 1
    for(c in id){
      num_ids <- length(id)
      print(paste("Extracting ids for", c, "cells"))
      
      out <- as_tibble(filter(allen_metadata_2, subclass_label == c & donor_sex_label == s))
      n_out <- length(which(out$subclass_label == c))
      print(paste("There are", n_out, c, "cells total."))
        
      if(n_out >= x){
        out <- sample_n(out, x)
      }
        
      if(n_out < x){
          out <- sample_n(out, n_out)
      }
      results_list[[z]] <- out
      z <- z + 1
      }
    results <- bind_rows(results_list)
    results <- results %>%
      dplyr::select(sample_name)
    filename <- paste0(i, "-", x, "-", s, "_all_subclass.txt")
    print(paste("Writing results:", filename))
      
    write.table(results$sample_name, file = paste0(outputs, filename),
                  quote = FALSE, row.names = FALSE, col.names = FALSE,
                  sep = "\t")
      }
    }
  }
}


# Non sex-specific
get_subsample_subclass_sexless <- function(id, num, seed){
  for(i in seed){
    print(paste("Sampling seed id:", i))
    set.seed(i)
  for(x in num){
    print(paste("Sampling a maximum of", x, "cells per cell type"))
    results_list <- list()
    z <- 1
    for(c in id){
      num_ids <- length(id)
      print(paste("Extracting ids for", c, "cells"))
      
      out <- as_tibble(filter(allen_metadata_2, subclass_label == c))
      n_out <- length(which(out$subclass_label == c))
      print(paste("There are", n_out, c, "cells total."))
        
      if(n_out >= x){
        out <- sample_n(out, x)
      }
        
      if(n_out < x){
          out <- sample_n(out, n_out)
      }
      results_list[[z]] <- out
      z <- z + 1
      }
    results <- bind_rows(results_list)
    results <- results %>%
      dplyr::select(sample_name)
    filename <- paste0(i, "-", x, "_all_subclass.txt")
    print(paste("Writing results:", filename))
      
    write.table(results$sample_name, file = paste0(outputs, filename),
                  quote = FALSE, row.names = FALSE, col.names = FALSE,
                  sep = "\t")
    }
  }
}

```

#### Make expressionset object
```{r}
make_exprsset <- function(in_dir, mat){
  print("Making the transposed matrix")
  matrix <- read.csv(paste0(in_dir, mat))
  matrix <- matrix %>%
    arrange(sample_name)
  rownames(matrix) <- matrix$sample_name
  matrix <- matrix %>%
    dplyr::select(-sample_name)
  print(paste("Were the rownames set?", head(rownames(matrix))))
  matrix <- as.matrix(matrix)
  matrix <- t(matrix)
  
  print("Generating the Allen metadata")
  temp_metadata <- allen_metadata_2 %>%
    filter(sample_name %in% colnames(matrix)) %>%
    arrange(sample_name)
  rownames(temp_metadata) <- temp_metadata$sample_name
  
  print("Making sure rownames of metadata match colnames of the matrix")
  if(all(rownames(temp_metadata) == colnames(matrix))){
    print("Temp matrix and phenodata are properly formatted")
  } else {
    stop("Temp matrix and phenodata are not properly formatted, make sure colnames and rownames of the respective objects are correct.")
  }
  
  print("Creating the expressionset object")
  annotated_metadata <- new("AnnotatedDataFrame", data = temp_metadata)
  expressionset_object <- ExpressionSet(assayData = matrix,
                                        phenoData = annotated_metadata)
  print("Saving the RDS file")
  saveRDS(expressionset_object, 
          file = paste0(outputs, mat, ".rds"))
}
```


### MuSiC Cell Proportion Estimates

Given a list of expressionset objects, generate a consolidated table of estimates for the mouse bulk-seq samples for each seed and sampling depth level

```{r}
generate_estimates <- function(obj, sexid){
  
  # Initializing list and index
  
  # Subsetting pheno data based on input sex
  print("generating the subsetted pheno_data from bulk-seq data")
  pheno_data <- pData(bulk_seq)
  pdata_sub <- pheno_data %>%
    dplyr::filter(sex == sexid)
  bulkseq_sub <- bulk_seq[, sampleNames(bulk_seq) %in% pdata_sub$sample_id]
  print(dim(pdata_sub))
  
  # Generating estimates
  
  print("reading in the RDS file for the single-cell expression set object")
  rds_obj <- readRDS(paste0(inputs, obj))
  cell_prop_estimates <- music_prop(bulk.eset = bulkseq_sub, 
                         sc.eset = rds_obj,
                         clusters = 'subclass_label',
                         sample = 'external_donor_name_label')
  
  # print("Formatting the results df")
  # estimate_df <- as.data.frame(cell_prop_estimates$Est.prop.weighted)
  # estimate_df <- tibble::rownames_to_column(estimate_df, var = "sample_id")
  # estimate_df <- estimate_df %>% 
  # left_join(pheno_data, by = "sample_id")
  
  return(cell_prop_estimates)
}

# Sexless ####
generate_estimates_sexless <- function(obj){
  
  # Initializing list and index
  
  # Subsetting pheno data based on input sex
  print("generating the subsetted pheno_data from bulk-seq data")
  pheno_data <- pData(bulk_seq)
  bulkseq_sub <- bulk_seq[, sampleNames(bulk_seq) %in% pheno_data$sample_id]
  print(dim(pheno_data))
  
  # Generating estimates
  
  print("reading in the RDS file for the single-cell expression set object")
  rds_obj <- readRDS(paste0(inputs, obj))
  cell_prop_estimates <- music_prop(bulk.eset = bulkseq_sub, 
                         sc.eset = rds_obj,
                         clusters = 'class_label',
                         sample = 'external_donor_name_label')
  
  # print("Formatting the results df")
  # estimate_df <- as.data.frame(cell_prop_estimates$Est.prop.weighted)
  # estimate_df <- tibble::rownames_to_column(estimate_df, var = "sample_id")
  # estimate_df <- estimate_df %>% 
  # left_join(pheno_data, by = "sample_id")
  
  return(cell_prop_estimates)
  }
```

```{r}
# linking to the metadata file directly because I don't want mulitiple half-gig copies on my computer 

allen_metadata <- vroom("/Users/sks36/Desktop/R/mouse_project/MuSiC/methods/inputs/metadata.csv") %>% clean_names()

# See what the distribution of subclass cells look like for each class
table(filter(allen_metadata, class_label == "GABAergic")$subclass_label)
table(filter(allen_metadata, class_label == "Glutamatergic")$subclass_label)
table(filter(allen_metadata, class_label == "Non-Neuronal")$subclass_label)
```



```{r}
allen_metadata_hip <- allen_metadata %>%
  filter(region_label == "HIP")

allen_metadata_2 <- allen_metadata %>%
  rowwise() %>%
  mutate(sub_id = ifelse(class_label == "Glutamatergic", "glut",
                         ifelse(class_label == "GABAergic", "gaba",
                                subclass_label)))
allen_metadata_2$sub_id <- recode(allen_metadata_2$sub_id, 
                                  "Oligo" = "oligo", "Astro" = "astro", 
                                  "SMC-Peri" = "smc_peri", "Endo" = "endo", 
                                  "VLMC" = "vlmc", 'Micro-PVM' = "micro_pvm")

allen_metadata_2 <- allen_metadata %>%
  filter(subclass_label != "")

subclass_to_include <- c("Oligo", "Astro", "Endo", "Micro_PVM", "SMC_Peri",
                         "VLMC", "Sst", "Lamp5", "Vip", "Pvalb", "Sncg", "Sst Chodl",
                         "CA1-ProS", "SUB-ProS", "CA2", "CA3", "DG")

# Final subsetted metadata file, excluding non-HPC Glutamatergic neurons and some of the very-low cell # classifications (Mies2 with one cell from one mouse). 

allen_metadata_2 <- allen_metadata_2 %>%
  dplyr::select(sample_name, donor_sex_label,
    external_donor_name_label, subclass_label,
    neighborhood_label, region_label)

unique(allen_metadata_2$sub_id)
unique(allen_metadata_2$subclass_label)
```


# Extract cells
```{r}
# Setting up the input variables for the subset function
seeds <- 19850212
counts <- c(2500)
cells <- unique(allen_metadata_2$subclass_label)
sex <- c("F", "M")

sink(paste0(outputs, "20210221_music_no_filtering_subclass_log.txt"), 
     append = FALSE, split = TRUE)
get_subsample_subclass(id = cells, sex = sex, 
              num = counts, seed = seeds)

sink()

sink(paste0(outputs, "music_no_filtering_subclass_mf2500_20210223_log.txt"), 
     append = FALSE, split = TRUE)
get_subsample_subclass_sexless(id = cells, num = counts, seed = seeds)

sink()
```


# Import the extracted matrices

```{r}
list.files(inputs)
make_exprsset(inputs, )
make_exprsset(paste0(inputs, "mat_subset_files/"), "1-100-F_all_subclass.txt_exprs.txt")
```

# Create cell estimates

```{r}
# Import bulkseq expressionset object 
bulk_seq <- readRDS("/Users/sks36/Desktop/R/mouse_project/MuSiC/methods/inputs/UNC_c58c57_GEX_expressionset.rds")

results_f <- generate_estimates("1-100-F_all_subclass.txt_exprs.txt.rds", "F")
results_m <- generate_estimates("1-100-M_all_subclass.txt_exprs.txt.rds", "M")
allen_rds <- readRDS(paste0(inputs, "music_estimate_complete_allen_2.5k_20210223.rds"))
results_class <- generate_estimates_sexless("music_estimate_complete_allen_2.5k_20210223.rds")

 


pheno_data <- pData(bulk_seq)
bulkseq_sub <- bulk_seq[, sampleNames(bulk_seq) %in% pheno_data$sample_id]
print(dim(pheno_data))
  
  # Generating estimates

allen_rds <- readRDS(paste0(inputs, "music_estimate_complete_allen_2.5k_20210223.rds"))
new_pheno_data <- as_tibble(pData(allen_rds))

new_pheno_data <- new_pheno_data %>%
  dplyr::select(sample_name) %>%
  left_join(allen_metadata, by = "sample_name")

pData(allen_rds) <- new_pheno_data
  
print("reading in the RDS file for the single-cell expression set object")

cell_prop_estimates <- music_prop(bulk.eset = bulkseq_sub, 
                       sc.eset = allen_rds, 
                       clusters = 'subclass_label', centered = TRUE, 
                       iter.max = 4000, normalize = TRUE,
                       sample = 'external_donor_name_label')
estimates <- cell_prop_estimates$Est.prop.weighted

# generate_results <- function(section){
#   temp_f <- as.data.frame(results_f[[section]])
#   temp_f <- tibble::rownames_to_column(temp_f, var = "sample_id")
#   temp_f <- temp_f %>%
#     left_join(pheno_data, by = "sample_id")
#   temp_m <- as.data.frame(results_m[[section]])
#   temp_m <- tibble::rownames_to_column(temp_m, var = "sample_id")
#   temp_m <- temp_m %>%
#     left_join(pheno_data, by = "sample_id")
#   final <- bind_rows(temp_f, temp_m)
#   return(final)
# }

options(digits=3, scipen = 999)
pheno_data <- pData(UNC_c58c57_GEX_expressionset)

# Cell proportion estimates
proportions <- as.data.frame(cell_prop_estimates$Est.prop.weighted)
proportions <- proportions %>%
  select_if(Negate(function(col) is.numeric(col) && mean(col) < 0.01)) %>% 
  tibble::rownames_to_column(var = "sample_id")

proportions_pheno <- proportions %>%
  left_join(pheno_data, by = "sample_id")

estimates_summary <- proportions_pheno %>%
  group_by(brain_region, sex, strain) %>%
  summarize_at(2:9, mean, na.rm = TRUE)

estimates_2 <- as.data.frame(estimates) %>%
  rownames_to_column("sample_id") %>%
  left_join(pheno_data, by = "sample_id")
estimates_summary_2 <- proportions_pheno %>%
  group_by(brain_region, sex, strain) %>%
  summarize_at(2:9, mean, na.rm = TRUE)


write.table(proportions_pheno, file = paste0(outputs, "MuSiC_2.5k_estimates_pheno_20210224.txt"),
            sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)

write.table(estimates_summary, file = paste0(outputs, "MUSIC_2.5k_estimates_summary_20210224.txt"),
            sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)
```



```{r}
library(tidyr)
library(viridis)
longer_results <- proportions_pheno %>%
  pivot_longer(2:9, names_to = "cell_type", values_to = "proportion")

longer_results_2 <- results_combined_fm %>%
  pivot_longer(2:14, names_to = "cell_type", values_to = "proportion")

my_theme <- theme(axis.text.x = element_text(hjust = 1, size = 14, angle = 45, face = "bold"),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 12, face = "bold"),
        axis.text.y = element_text(size = 14, face = "bold"),
        axis.title = element_text(size = 14, face = "bold"))
```

# Sex differences between regions / strains

# Strain - Amygdala 
```{r}
strain_diff_amy <- ggplot(data = dplyr::filter(longer_results, brain_region == "A"),
                          aes_string(x = "cell_type", y = "proportion")) +
  geom_boxplot(alpha = 0.5,
               aes(color = strain)) +
  geom_point(aes(color = strain, fill = strain),
           position = position_dodge(0.8)) + 
  xlab("") +
  ylab("Estimated Cell-Type Proportion") +
  ggtitle("Strain") +
  labs(subtitle = "Amygdala") +
  ylim(0, 0.5) +
  theme_classic() +
  my_theme +
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 
```

# Strain - Hippocampus 
```{r}
strain_diff_hip <- ggplot(data = dplyr::filter(longer_results, brain_region == "H"),
                          aes_string(x = "cell_type", y = "proportion")) +
  geom_boxplot(alpha = 0.5,
               aes(color = strain)) +
  geom_point(aes(color = strain, fill = strain),
           position = position_dodge(0.8)) + 
  xlab("") +
  ylab("Estimated Cell-Type Proportion") +
  ggtitle("Strain") +
  labs(subtitle = "Hippocampus") +
  ylim(0, 0.5) +
  theme_classic() +
  my_theme +
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 
```
# Social - Amygdala 
```{r}
soc_diff_amy <- ggplot(data = dplyr::filter(longer_results, brain_region == "A" &
                                              strain == "C58J"),
                          aes_string(x = "cell_type", y = "proportion")) +
  geom_boxplot(alpha = 0.5,
               aes(color = sociability)) +
  geom_point(aes(color = sociability, fill = sociability),
           position = position_dodge(0.8)) + 
  xlab("") +
  ylab("Estimated Cell-Type Proportion") +
  ggtitle("C58J Sociability") +
  labs(subtitle = "Amygdala") +
  ylim(0, 0.5) +
  theme_classic() +
  my_theme + 
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 
```

# Social - Hippocampus 
```{r}
soc_diff_hip <- ggplot(data = dplyr::filter(longer_results, brain_region == "H" &
                                              strain == "C58J"),
                          aes_string(x = "cell_type", y = "proportion")) +
  geom_boxplot(alpha = 0.5,
               aes(color = sociability)) +
  geom_point(aes(color = sociability, fill = sociability),
           position = position_dodge(0.8)) + 
  xlab("") +
  ylab("Estimated Cell-Type Proportion") +
  ggtitle("C58J Sociability") +
  labs(subtitle = "Hippocampus") +
  ylim(0, 0.5) +
  theme_classic() +
  my_theme +
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 
```


```{r}
# Combining the sex / region plots ####

library(cowplot)

strain_legend <- get_legend(strain_diff_hip + theme(legend.box.margin = margin(0, 0, 0, 12)))
social_legend <- get_legend(soc_diff_hip + theme(legend.box.margin = margin(0, 0, 0, 12)))

strain <- plot_grid(
  strain_diff_amy + theme(legend.position = "none"),
  strain_diff_hip + theme(legend.position = "none") + ylab(NULL),
  align = 'hv',
  labels = c("A", "B"),
  hjust = -1,
  nrow = 1
)

social <- plot_grid(
  soc_diff_amy + theme(legend.position = "none"),
  soc_diff_hip + theme(legend.position = "none") + ylab(NULL),
  align = 'hv',
  labels = c("C", "D"),
  hjust = -1,
  nrow = 1
)


grid_plot <- plot_grid(strain, strain_legend, 
                       social, social_legend,
                       nrow = 2,
                       ncol = 2,
                       rel_widths = c(1, 0.1))

ggsave(filename = paste0(outputs, "mofa_estimates_strain_sociability_20210302.png"),
       plot = grid_plot, dpi = 100, width = 10, height = 10, units = "in")

ggsave(filename = paste0(outputs, "20210218_C58_cell_estimates_by_strain_sex_mf.png"),
       plot = sex_block_2, dpi = 100, width = 18, height = 8, units = "in")

```


# FM followup tables & plots
The FM dataset showed a clear shift towards male estimates when I included the male reference for some but not all cell classes. I want to dig into these to see if they're a result of poor coverage for female cells for a given class, or a legitimate case for sex-specific reference datasets. 

```{r}
sex_count_table <- allen_metadata_2 %>%
  group_by(donor_sex_label, subclass_label) %>%
  count()

individual_count_table <- allen_metadata_2 %>%
  group_by(donor_sex_label, subclass_label) %>%
  summarise(unique_individuals = n_distinct(external_donor_name_label))


sample_id_m <- read.csv(file = paste0(inputs,"2121985-5000-M_all_subclass.txt"),
                         col.names = "id")
sample_id_f <- read.csv(file = paste0(inputs, "2121985-5000-F_all_subclass.txt"),
                        col.names = "id")
sample_ids <- bind_rows(sample_id_m, sample_id_f)
subbed_allen_meta <- filter(allen_metadata_2,
                            sample_name %in% sample_ids$id)

sampled_sex_count_table <- subbed_allen_meta %>%
  group_by(donor_sex_label, subclass_label) %>%
  count()

sampled_individual_count_table <- subbed_allen_meta %>%
  group_by(donor_sex_label, subclass_label) %>%
  summarise(unique_individuals = n_distinct(external_donor_name_label))





# Plotting the number of cells for each sex in the reference dataset
cells_by_sex <- ggplot(data = sex_count_table, 
                       aes_string(x = "subclass_label", y = "n", fill = "donor_sex_label")) +
  geom_bar(stat='identity', position='dodge', aes(color = donor_sex_label)) +
  xlab("") +
  ylab("# Cells") +
  ggtitle("Total Number of Cells Per Cell-Type by Sex") +
  labs(subtitle = "") +
  geom_hline(yintercept = 5000, linetype = "dashed", color = "red") +
  #ylim() +
  theme_classic() +
  theme(axis.text.x = element_text(hjust = 1, size = 14, angle = 45, face = "bold"),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 16, face = "bold"),
        axis.text.y = element_text(size = 14, face = "bold"),
        axis.title = element_text(size = 14, face = "bold")) +
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 

# By unique IDs
cells_by_individual <- ggplot(data = individual_count_table, 
                       aes_string(x = "subclass_label", 
                                  y = "unique_individuals", 
                                  fill = "donor_sex_label")) +
  geom_bar(stat='identity', position='dodge', aes(color = donor_sex_label)) +
  xlab("") +
  ylab("# Subjects") +
  scale_y_continuous(breaks=seq(0,30,5)) +
  ggtitle("Total Number of Subjects Per Cell-Type by Sex") +
  labs(subtitle = "") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  #ylim() +
  theme_classic() +
  theme(axis.text.x = element_text(hjust = 1, size = 14, angle = 45, face = "bold"),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 16, face = "bold"),
        axis.text.y = element_text(size = 14, face = "bold"),
        axis.title = element_text(size = 14, face = "bold")) +
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 

# Plotting sampled cells for each sex 
subcells_by_sex <- ggplot(data = sampled_sex_count_table, 
                       aes_string(x = "subclass_label", y = "n", fill = "donor_sex_label")) +
  geom_bar(stat='identity', position='dodge', aes(color = donor_sex_label)) +
  xlab("") +
  ylab("# Cells") +
  ggtitle("Total Number of Subsampled Cells Per Cell-Type by Sex") +
  labs(subtitle = "") +
  #ylim() +
  theme_classic() +
  theme(axis.text.x = element_text(hjust = 1, size = 14, angle = 45, face = "bold"),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 16, face = "bold"),
        axis.text.y = element_text(size = 14, face = "bold"),
        axis.title = element_text(size = 14, face = "bold")) +
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 

# By sampled cells by unique IDs
subcells_by_individual <- ggplot(data = sampled_individual_count_table, 
                       aes_string(x = "subclass_label", 
                                  y = "unique_individuals", 
                                  fill = "donor_sex_label")) +
  geom_bar(stat='identity', position='dodge', aes(color = donor_sex_label)) +
  xlab("") +
  ylab("# Subjects") +
  scale_y_continuous(breaks=seq(0,30,5)) +
  ggtitle("Total Number of Subsampled Subjects Per Cell-Type by Sex") +
  labs(subtitle = "") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  #ylim() +
  theme_classic() +
  theme(axis.text.x = element_text(hjust = 1, size = 14, angle = 45, face = "bold"),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 16, face = "bold"),
        axis.text.y = element_text(size = 14, face = "bold"),
        axis.title = element_text(size = 14, face = "bold")) +
  scale_color_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) +
  scale_fill_viridis(discrete = TRUE, option = "D", begin = 0, end = .8) 

# Combining the sex / region plots ####
# create some space to the left of the legend

cells_plots_1 <- plot_grid(
  cells_by_sex + theme(legend.position="none"),
  cells_by_individual + theme(legend.position="none"),
  align = 'hv',
  #labels = c("A", "B"),
  hjust = -1,
  nrow = 1
)

cells_plots_2 <- plot_grid(
  subcells_by_sex + theme(legend.position="none"),
  subcells_by_individual + theme(legend.position="none"),
  align = 'hv',
  #labels = c("A", "B"),
  hjust = -1,
  nrow = 1
)



legend <- get_legend(cells_by_sex + theme(legend.box.margin = margin(0, 0, 0, 12)))
cells_plots_1 <- plot_grid(cells_plots_1, legend, rel_widths = c(1, 0.08))
cells_plots_2 <- plot_grid(cells_plots_2, legend, rel_widths = c(1, 0.08))
ggsave(filename = paste0(outputs, "20210218_cell_ind_counts_primary.png"),
       plot = cells_plots_1, dpi = 100, width = 18, height = 8, units = "in")

ggsave(filename = paste0(outputs, "20210218_cell_ind_counts_subset.png"),
       plot = cells_plots_2, dpi = 100, width = 18, height = 8, units = "in")
```


# Sankey QC pipe

```{r}
library(patchwork)
library(hrbrthemes)
library(circlize)
library(networkD3)

# Make a connection data frame
allen_cells <- allen_metadata %>%
    filter(!is.na(subclass_label)) %>%
    group_by(subclass_label) %>% count()

final_cells <- subbed_allen_meta %>%
    filter(!is.na(subclass_label)) %>%
    group_by(subclass_label) %>% count()

used_cells <- filter(allen_cells, subclass_label %in% subbed_allen_meta$subclass_label)

links <- data.frame(
  source = c("All Allen Cells", allen_cells$subclass_label) 
)
new_cols <- c("source", sprintf("f%02d", seq(1,43)))

links[,new_cols] <- ""
links[,1] <- c("All Allen Cells", allen_cells$subclass_label)
links <- links %>%
  rowwise() %>%
  mutate(f01 = ifelse(source %in% used_cells$subclass_label, 
                      "Included", "Excluded")) %>%
  mutate(f02 = ifelse(source %in% used_cells$subclass_label,
                      "Final Dataset", ""))
links[1,2:44] <- as.list(allen_cells$subclass_label)

links_long <- links %>%
  pivot_longer(2:44, names_to = "target") %>%
  dplyr::select(-target) %>%
  filter(value != "") %>%
  rename("value" = "target")

# now add the values to the df conditionally based on the transfer
links_long_allen <- links_long %>%
  filter(source == "All Allen Cells") %>%
  left_join(allen_cells, by = c("target" = "subclass_label")) %>%
  rename("n" = "value")

links_long_filter <- links_long %>%
  filter(target == "Included" | target == "Excluded") %>%
  left_join(allen_cells, by = c("source" = "subclass_label")) %>%
  rename("n" = "value")

links_long_final <- links_long %>%
  filter(target == "Final Dataset") %>%
  left_join(final_cells, by = c("source" = "subclass_label")) %>%
  rename("n" = "value")

links_long <- bind_rows(links_long_allen, links_long_filter)
links_long <- links_long %>%
  add_row(source = "Included", target = "Final Dataset", value = 84729)

rm(links_long_allen, links_long_filter, links, new_cols, used_cells)
  
# From these flows we need to create a node data frame: it lists every entities involved in the flow
nodes <- data.frame(
  name=c(as.character(links_long$source), as.character(links_long$target)) %>% 
    unique()
)

# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
links_long$IDsource <- match(links_long$source, nodes$name)-1 
links_long$IDtarget <- match(links_long$target, nodes$name)-1
 
color_scale ='d3.scaleOrdinal() .range(["#FDE725FF","#B4DE2CFF","#6DCD59FF","#35B779FF","#1F9E89FF","#26828EFF","#31688EFF","#3E4A89FF","#482878FF","#440154FF"])'
# Thus we can plot it
p <- sankeyNetwork(Links = links_long, Nodes = nodes, Source = "IDsource",
              Target = "IDtarget", Value = "value", iterations = 10,
              NodeID = "name", colourScale = color_scale,
              sinksRight = TRUE, nodeWidth = 60, margin = 10, fontSize = 60, 
              nodePadding = 35, units = "cells", height = 2000, 
              width = 4000)
p

# save the widget
library(htmlwidgets)
saveWidget(p, file=paste0(outputs, "sankeycells.html"))

library(webshot2)
webshot(paste0(outputs, "sankeycells.html"), 
        paste0(outputs,"sankeycells.png"), 
        delay = 2, vwidth = 4000, vheight = 2000, cliprect = "viewport")

```


```{r}
library(multiClust)
```

# Fucking make a table
```{r}
library(gt)
library(webshot)

options(digits = 3, scipen = 999)

# Making a table of the cell counts for the Allen Reference dataset ####

allen_estimates_male_a <- estimates_summary_2 %>%
  filter(sex == "M" & brain_region == "a") 

allen_estimates_female_a <- estimates_summary_2 %>%
  filter(sex == "F" & brain_region == "a") 

allen_estimates_male_h <- estimates_summary_2 %>%
  filter(sex == "M" & brain_region == "h") 

allen_estimates_female_h <- estimates_summary_2 %>%
  filter(sex == "F" & brain_region == "h") 



allen_estimates_2 <- full_join(allen_estimates_female, allen_estimates_male) %>%
  arrange(strain)
allen_estimates_final <- t(allen_estimates_2)

library(gt)

allen_estimates_table <- allen_estimates_2 %>% 
  gt(groupname_col = "strain", auto_align = TRUE) %>%
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_column_labels(everything())) %>%
  opt_table_lines(extent = "default") %>%
  tab_header(
    title = md("Neuronal Cell Proportion Estimates")) %>%
  # tab_spanner(label = "Females",
  #             columns = 3:8) %>%
  # tab_spanner(label = "Males",
  #             columns = 9:14) %>%
  cols_label(brain_region = "Brain Region",
             sex = "Sex",
             strain = "Strain") %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.top.width = px(0),
    column_labels.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.bottom.color = "white",
    table.border.bottom.width = px(0),
    data_row.padding = px(0),
    column_labels.font.size = 12,
    table.font.size = 10,
    column_labels.font.weight = "bold",
    row_group.background.color = "black",
    row.striping.include_table_body = TRUE,
    row.striping.background_color = "#eaeaea"
    #table.font.size = 2
    #container.width = px(1400),
    #row_group.padding = px(-3)
    
    #container.height = pct(100)
  )


gtsave(allen_estimates_table, 
       filename = "allen_cell_prop_table.png", 
       path = "/Users/sks36/Desktop/R/mouse_project/MuSiC/subclass_estimates/outputs")


# Making a table of the cell cell estimate results ####

results_table <- results_combined %>%
  dplyr::select(sample_id, strain, brain_region, sex, sociability, 2:14)

results_table <- results_table[1:20,] %>% 
  gt(auto_align = TRUE) %>%
  #cols_width(vars("Global AF") ~ pct(10),
  #           vars("Association") ~ pct(60)) %>%
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_column_labels(everything())) %>%
  #tab_style(style = list(cell_fill(color = "#b1fffb")),
  #          locations = cells_body(rows = c(5,16,34,38))) %>%
  opt_table_lines(extent = "default") %>%
  tab_header(
    title = md("MuSiC Results Table")) %>%
  #tab_spanner(label = "Females",
  #            columns = 3:8) %>%
  # tab_spanner(label = "Males",
  #             columns = 9:14) %>%
  # cols_label(subclass_label = "cell classification",
  #            total_m = "total",
  #            mean_m = "mean",
  #            sd_m = "sd",
  #            min_m = "min",
  #            max_m = "max",
  #            'n mice m' = "n mice") %>%
  tab_options(
    column_labels.border.top.color = "black",
    column_labels.border.top.width = px(0),
    column_labels.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.bottom.color = "white",
    table.border.bottom.width = px(0),
    data_row.padding = px(0),
    column_labels.font.size = 12,
    table.font.size = 10,
    column_labels.font.weight = "bold",
    row_group.background.color = "black",
    row.striping.include_table_body = TRUE,
    row.striping.background_color = "#eaeaea"
    #table.font.size = 2
    container.width = px(1200)
    #row_group.padding = px(-3)
    
    #container.height = pct(100)
  )


gtsave(results_table, 
       filename = "20210219_MuSiC_short_results_table.png", 
       path = outputs)


```

